\documentclass{sig-alternate-05-2015}
\usepackage{tabularx,colortbl}
\usepackage[dvipsnames]{xcolor}
\usepackage{flushend}
\usepackage{cite}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{stmaryrd}
\usepackage{url}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{comment}
\usepackage{longtable}
\usepackage{supertabular}
\usepackage{times}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{color}
\usepackage{balance}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}


\newcommand{\mkeyword}[1]{\mbox{\texttt{#1}}}
\DeclareMathOperator{\kuop}{uop}
\DeclareMathOperator{\kbop}{bop}
\DeclareMathOperator{\kite}{ite}
\DeclareMathOperator{\kpre}{pre}
\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\ktrue}{true}
\DeclareMathOperator{\kfalse}{false}
\DeclareMathOperator{\kselect}{select}
\DeclareMathOperator{\ran}{range}
\newcommand{\lbb}{[\![}
\newcommand{\rbb}{]\!]}
\newcommand{\expr}{\phi}
\newcommand{\exprS}{\Phi}
% this toggles between a tech-report version of the paper and the MEMOCODE version
%\newcommand{\TECHREPORT}{}
%\tolerance=1
%\emergencystretch=\maxdimen
%\hyphenpenalty=10000
%\hbadness=10000
\sloppypar


\begin{document}
\CopyrightYear{2017}
\setcopyright{acmcopyright}
\conferenceinfo{}{ }
\isbn{ }\acmPrice{ }
\doi{ }
 % Add this to every tex file, so that you can comment with a diff color%
\definecolor{gold}{rgb}{0.90,.66,0}
\definecolor{dgreen}{rgb}{0,0.6,0}
\newcommand{\mike}[1]{\textcolor{red}{#1}}
\newcommand{\fixed}[1]{\textcolor{purple}{#1}}
\newcommand{\andrew}[1]{\textcolor{green}{#1}}
\newcommand{\ela}[1]{\textcolor{blue}{#1}}
\newcommand{\stateequiv}{\equiv_{s}}
\newcommand{\traceequiv}{\equiv_{\sigma}}
\newcommand{\ta}{\text{TA}}
\newcommand{\cta}{\text{TA$_{C}$}}
\newcommand{\tta}{\text{TA$_{T}$}}
\newcommand{\nondetcov}{\text{\sc Nondet-Cov}}
\newcommand{\nondetcovalt}{\text{\sc Nondet-Cov$^{*}$}}
\newcommand{\ivccov}{\text{\sc IVC-Cov}}
\newcommand{\maycov}{\text{\sc May-Cov}}
\newcommand{\mustcov}{\text{\sc Must-Cov}}
\newcommand{\allcov}{\text{\sc Model-Cov}}
\newcommand{\mutcov}{\text{\sc Mutant-Cov}}
\newcommand{\bfalg}{{IVC\_BF}\xspace}
\newcommand{\ucalg}{{IVC\_UC}\xspace}
\newcommand{\ucbfalg}{{IVC\_UCBF}\xspace}
\newcommand{\mustalg}{{IVC\_MUST}\xspace}
\newdef{lemma}{Lemma}
\newdef{definition}{Definition}
\newdef{coroll}{Corollary}
\newdef{theorem}{Theorem}
\newdef{note}{Note}
%\newcommand{\TECHREPORT}{}

\title{Proof-based Coverage Metrics for Formal Verification}

\numberofauthors{2}

\author{
\alignauthor
Elaheh Ghassabani\\
       \affaddr{Department of Computer Science and Engineering}\\
       \affaddr{University of Minnesota}\\
       \affaddr{\small{200 Union Street\\Minneapolis, MN, 55455, USA}}\\
       \email{\texttt{\small{ghass013@umn.edu}}}
\alignauthor
Andrew Gacek\\
       \affaddr{Rockwell Collins\\ Advanced Technology Center}\\
       \affaddr{\small{400 Collins Rd. NE\\Cedar Rapids, IA, 52498, USA}}\\
       \email{\texttt{\small{andrew.gacek@rockwellcollins.com}}}\\
       \and
\alignauthor
Michael W. Whalen\\
       \affaddr{Department of Computer Science and Engineering}\\
       \affaddr{University of Minnesota}\\
       \affaddr{\small{200 Union Street\\Minneapolis, MN, 55455, USA}}\\
       \email{\texttt{\small{whalen@cs.umn.edu}}}
\alignauthor
Mats Heimdahl\\
       \affaddr{Department of Computer Science and Engineering}\\
       \affaddr{University of Minnesota}\\
       \affaddr{\small{200 Union Street\\Minneapolis, MN, 55455, USA}}\\
       \email{\texttt{\small{heimdahl@cs.umn.edu}}}
} 
\maketitle




\begin{abstract}
 An important question while using formal verification is whether we have specified enough properties for a given implementation model.  To address this question, we need coverage metrics for property-based formal verification. Existing metrics are usually based on mutation, in which the implementation model is modified and re-analyzed to determine whether the properties hold over the mutated model.
 However, these metrics are expensive to compute (involving many additional proofs), and have the issue that the residual model after removing the ``unnecessary'' parts is often inadequate to prove the original property. This paper proposes an alternate characterization of completeness based on the proofs themselves.   We have previously investigated algorithms for determining minimal sets of model elements necessary to construct safety-property proofs called Inductive Validity Cores (IVCs).  In this paper, we examine a family of coverage metrics that can be computed from IVCs.  One of the proposed metrics is substantially cheaper to compute than previous metrics and is guaranteed to preserve a residual model that leads to a proof.  Other possible metrics are more expensive to compute and provide  more- or less-rigorous definitions.
 We demonstrate the metrics on a large corpus of examples.

\end{abstract}


%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10003752.10003790.10003794</concept_id>
%<concept_desc>Theory of computation~Automated reasoning</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10003752.10003790.10011192</concept_id>
%<concept_desc>Theory of computation~Verification by model checking</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10011074.10011075.10011076</concept_id>
%<concept_desc>Software and its engineering~Requirements analysis</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10011007.10011074.10011099.10011692</concept_id>
%<concept_desc>Software and its engineering~Formal software verification</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Theory of computation~Verification by model checking}
%\ccsdesc[500]{Theory of computation~Automated reasoning}
%\ccsdesc[500]{Software and its engineering~Requirements analysis}
%\ccsdesc[500]{Software and its engineering~Formal software verification}
%\printccsdesc
\keywords{coverage; requirements completeness; formal verification; SAT-based model checking;
  inductive proofs; inductive validity cores;}

 

\input{introduction}

%\ifdefined\TECHREPORT
%\input{description}
%\fi
\input{example}

%\input{background}

\input{formalization}

\input{method}

\input{Illustration}

\input{impl}

\input{experiments}

\input{discussion}

\input{related}

\input{conclusion}

%\section*{Acknowledgment}
%
%
%The authors would like to thank...
%more thanks here


\bibliographystyle{abbrv}
\bibliography{biblio}

% This ~ seems to fix an odd bibliography alignment issue
~
\end{document}


