%\subsection{Experiment}
%\label{sec:experiment}

\newcommand{\takeaway}[1]{
\vspace{6pt}
\noindent\fbox{\parbox{\textwidth}{#1}}
\vspace{6pt}
}
\subsection{Experimental Setup}
 In this study, we designed an experiment from
 the same benchmark suite used for evaluation of the \ucalg ~and \ucbfalg ~algorithms in \cite{Ghass16}.
 The benchmark contains 476 Lustre models
 from~\cite{Hagen08:FMCAD} and \cite{QFCS15:backes,hilt2013}.
 Most of
the benchmark models from~\cite{Hagen08:FMCAD} are small (10kB or less,
with 6-40 equations) and include a range of hardware benchmarks and
software problems involving counters.
However, models from \cite{QFCS15:backes,hilt2013} are industrial cases with over 600 equations around 80kB.
Each benchmark model has a single property to analyze.
For each test model, we computed \aivcalg , \ucalg , and \ucbfalg ~algorithms
in a configuration with
the \texttt{Z3} solver and the fastest mode of \texttt{JKind} (running K-induction and PDR in parallel). The experiments
were run on an  Intel(R) i5-4690, 3.50GHz,
16 GB memory machine.
%\footnote{\noindent ~The benchmarks, all raw experimental results,
%  and computed data are available on \cite{expr}.}

We would like to evaluate the efficiency
 of our algorithms and compare it with the \ucalg ~and \ucbfalg ~algorithms.
 Efficiency is computed in terms of wall-clock time. Therefore, we investigate the following research questions:
\begin{itemize}
  \item \textbf{RQ1)} How does the \aivcalg ~algorithm perform compared to the \ucalg ~and \ucbfalg ~algorithms?
  \item \textbf{RQ2)} How is the \aivcalg ~algorithm affected by the number of IVCs (diversity) and verification time (time a property takes to be proved)?
%
%  \item \textbf{RQ3)} How does approximating minimality influence the performance of the \aivcalg ~algorithm?
%  In other words, we would like to determine, for the implementation of the \getivc ~procedure, whether it would be better to use \ucalg ~or \ucbfalg .
%  \item \textbf{RQ4)} How did the pre-set timeout manifest itself in the experimental results?
\end{itemize}


\subsection{Experimental Results}

\input{results} 