This thesis is a milestone in four joyful years of work with amazing UMN Critical Systems Group (CriSys). My experience at UMN has been nothing short of spectacular. Since my first day on August 20th, 2014 I have felt at home at UMN with meeting my warm-hearted and caring advisors and friends. I have been given unique opportunities and taken
advantage of them. This includes being part of the cutting-edge projects while serving as a graduate research assistant at CriSys, attending a lot of top-tier conferences, meeting with the best researchers in my field, and on top of all, learning from many distinguished and knowledgeable professors at UMN. I would like to extend thanks to the many people who so generously contributed to the work presented in this thesis.

Special mention goes to my enthusiastic supervisor, Michael Whalen. My PhD has been an amazing experience and I thank Michael, not only for his tremendous academic support, but also for giving me so many wonderful opportunities. I would like to express my sincere gratitude to him for the continuous support of my Ph.D study and related research, for his patience, motivation, and immense knowledge.

Similar, profound gratitude goes to Mats Heimdahl, who has been a truly supportive co-advisor. I am particularly indebted to him for his constant faith in my work and for his support. I have very fond memories of my time with Michael and Mats, who have been like my family all these years. Their guidance helped me in all the time of research and writing of this thesis. I could not have imagined having a better advisor and mentor for my graduate studies.

Besides my advisors, I would like to thank the rest of my thesis committee: Prof. Stephen McCamant, Prof. Marc Riedel, and Prof. Eric Van Wyk, for their insightful comments and encouragement to widen my research from various perspectives.

I thank my fellow labmates for the stimulating discussions, for the sleepless nights we were working together before deadlines, and for all the fun we have had in the last four years. Also I thank the wonderful people in other organizations I had the opportunity to work with; in particular, I am grateful to Dr. Andrew Gacek and Jaroslav Bendik.

Last but not least, I would like to thank my loving family: my parents and my sisters for supporting me spiritually throughout writing this thesis and my my life in general. 